### 2024-03-06 manuscript.tex
Updated path to hierarchy figure
Corrected small typo by clarifying log likelihood ratio

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hierarchy/out/hierarchy.png}
\centering
\caption{\textbf{Hierarchical clustering of evolutionary signatures.}
Clusters are indicated by rectangles on the right. Clusters with fewer than 75 regions are omitted for clarity.}
\label{fig:hierarchy}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{clusters/out/clusters.png}
\centering
\caption{\textbf{Example clusters with log likelihood ratios and normalized optimal values.}
Each panel shows the pattern of log likelihoods of the indicated cluster from Fig~\ref{fig:hierarchy} in the upper half and the corresponding normalized estimated optimal values in the lower half. The optimal values are expressed as $z$-scores relative to each feature distribution in the subset of rapidly evolving disorder regions clustered in Fig~\ref{fig:hierarchy}. Values below or above negative or positive three are indicated with magenta and cyan, respectively.}
\label{fig:clusters}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hierarchy/out/hierarchy_delta_loglikelihood.png}
\centering
\caption{\textbf{Hierarchical clustering of evolutionary signatures.}
Clusters are indicated by rectangles on the right. Clusters with fewer than 75 regions are omitted for clarity.}
\label{fig:hierarchy}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{clusters/out/clusters.png}
\centering
\caption{\textbf{Example clusters with log likelihood ratios and normalized optimal values.}
Each panel shows the pattern of log likelihood ratios of the indicated cluster from Fig~\ref{fig:hierarchy} in the upper half and the corresponding normalized estimated optimal values in the lower half. The optimal values are expressed as $z$-scores relative to each feature distribution in the subset of rapidly evolving disorder regions clustered in Fig~\ref{fig:hierarchy}. Values below or above negative or positive three are indicated with magenta and cyan, respectively.}
\label{fig:clusters}
\end{figure}
